Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Changed ethnicity labels for retro histogram and pie chart

dat.retro %>% 
  ggplot(aes(x = Ethnicity_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the retro cohorts",
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

>>>>

dat.retro %>% 
  ggplot(aes(x = Ethnicity_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the retro cohorts",
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

dat.retro_ethnicity_pie <- dat.retro_ethnicity_pie %>% 
  mutate(Ethnicity_collapsed = 
           fct_recode(Ethnicity_collapsed,
             "White" = "European",
             "Asian or Asian British" = "Asian or Asian British",
             "Black or Black British" = "African or African British",
             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
             "Other" = "Other"
           ))
